The Speed of Evolution in a Two Dimensional Trait Space

### 2016-12-09 manuscript.tex
small updates to bib and manuscript.

@@

%-----------------------------------------------------------------------------------------
\section*{Methods}
\subsection*{Model Description}
The construction of our model employs much of the theoretical framework developed by Desai and Fisher \citep{DesFish07}, but with the key distinction of including two traits that evolve through selective and mutation forces.  We consider asexual populations with no recombination, and assume

\subsection*{Parameters, Model Basics, and Definitions}
The population size $N$ is assumed to large but fixed.  Beneficial mutations occur at a rate $U_k$, where $k=1,2$ designates the trait.  A beneficial mutation modifying trait $k$ provides a fixed incremental gain $\Delta c_k$, in the relative growth rate $r_{i,j}$ of a mutant, where $r_{i,j}=1+\Delta c_1 i + \Delta c_2 j$.  We adopt the convention of using an index $i$ and $j$ to indicate the number of beneficial mutations in the first and second trait, respectively.  The fitness of an individual or a fitness class can be represented as the point $(i,j) \in \mathbb{N}^2$.

Relative fitness is defined as its growth rate in excess of the population's mean growth rate $r_{i,j}-\bar{r}$, .  The mean fitness of a population can also be written as $\bar{r}=1+\Delta c_1 \bar{i} + \Delta c_2 \bar{j}$, where the means are marginal with respect to the joint distribution $p_{i,j}$.

@@

\subsection*{Adaptation in Two Dimensions}
%
The population is divided into subpopulations, called fitness classes, which

>>>>

\begin{abstract}
This paper will discuss something.
\end{abstract}

@@

%-----------------------------------------------------------------------------------------
\section*{Methods}
\subsection*{A Two Trait Model with Selection and Mutations}
The construction of our model employs much of the theoretical framework developed by Desai and Fisher \citep{DesFish07}, but with the key distinction of including two traits that evolve through selective and mutation forces.  We consider asexual populations with no recombination.  We assume that the population size $N$ large but fixed.  Beneficial mutations occur at a rate $U_k$, where $k=1,2$ and designates the trait in question.  A beneficial mutation modifying trait $k$ provides a fixed incremental gain $\Delta c_k$, in the relative growth rate $r_{i,j}$ of a mutant, where $r_{i,j}=1+\Delta c_1 i + \Delta c_2 j$.  We adopt the convention of using an indices $i$ and $j$ to indicate the number of beneficial mutations in the first and second trait, respectively.  This allows us to represent the fitness of an individual, or its fitness class, by a the point $(i,j) \in \mathbb{N}^2$.  The discrete fitness distribution of the population in the two dimensional trait space is then given by the set of frequencies $\{p_{i,j}\}_{i,j}$.  Relative fitness is defined as its growth rate in excess of the population's mean growth rate $r_{i,j}-\bar{r}$, .  The mean fitness of a population can also be written as $\bar{r}=1+\Delta c_1 \bar{i} + \Delta c_2 \bar{j}$, where the means are marginal with respect to the joint distribution $p_{i,j}$.

@@
